Soal Latihan

### 2021-10-20 Semester I/Analisis Numerik Lanjut/latihan/readme.Rmd
newdone

while(i <= iter_max && abs(p-x_0) > tol_max){
  p = x_0 - (f(x_0) / df(x_0))
  hasil[i+1,] = list(i,p)
  x_0 = p
  i = i + 1
}

@@

>>>>

while(i <= iter_max){
  p = x_0 - (f(x_0) / df(x_0))
  hasil[i+1,] = list(i,p)
  if(abs(p-x_0) > tol_max){break}
  x_0 = p
  i = i + 1
}

@@

Nilai `p` pada iterasi terakhir adalah akar yang kita cari.
